\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\begin{figure}[h]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:first}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}
}%
\subfigure[MR10 adapt mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}
}\\
\subfigure[MR10 adapt mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}\\
\end{center}
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}
}%
\subfigure[MR10 fixed adapt start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
}\\
\subfigure[MR10 fixed mesh t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
}%
\subfigure[MR10 fixed adapt t=1500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
}\\
\subfigure[MR10 fixed mesh t=7500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}
}%
\subfigure[MR10 fixed adapt t=7500]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}
}\\
\subfigure[MR10 fixed adapt end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}
}\\
\end{center}
\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
\label{fig:3testcase}
\end{figure}

>>>>

\begin{figure}[h]
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}%
}}%
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2testcase}
\end{figure}

@@

\begin{figure}[h]
\makebox[\textwidth]{%
\subfigure[[MR10 fixed mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh start]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh t=1500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh t=1500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh t=7500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}%
}%
\hfill    
\subfigure[MR10 adapt mesh t=7500]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR10 fixed mesh end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}%
}%
\hfill    
\subfigure[MR10 fixed adapt end]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}%
}}%
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
%\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
\label{fig:3testcase}
\end{figure}
